Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-24 RNARedPrint.tex
edit caption of toy tree decomp figure

\begin{figure}
{\centering \includegraphics[width=.9\linewidth]{Figs/example-treedec-stacking}\\}
\caption{\revised{Toy example of a tree decomposition associated with two target structures in the stacking energy model. Two target secondary structures ({\bfseries\sffamily A}) are merged into a joint hypergraph ({\bfseries\sffamily B}), whose hyperedges correspond to the quadruplets of positions involved in base pair stacks (colored). A valid tree decomposition ({\bfseries\sffamily C}) for the hypergraph ensures, among other properties, that each base pair and each base pair stack is represented in at least one of its node, so that features can be adequately evaluated. The treewidth of this tree decomposition is 3, a provably optimal value for this input hypergraph.}\label{fig:treedec}}
\end{figure}

>>>>

\begin{figure}
{\centering \includegraphics[width=.9\linewidth]{Figs/example-treedec-stacking}\\}
\caption{\revised{Toy example of a tree decomposition associated with two target structures in the stacking energy model (where the four positions of each base pair stack depend on each other). Two target secondary structures ({\bfseries\sffamily A}) are merged into a joint hypergraph ({\bfseries\sffamily B}), whose hyperedges correspond to the quadruplets of positions involved in base pair stacks (colored). A valid tree decomposition ({\bfseries\sffamily C}) for the hypergraph ensures, among other properties, that each base pair and each base pair stack is represented in at least one of its node, so that features can be correctly evaluated. The treewidth of this tree decomposition is 3, a provably optimal value for this input hypergraph.}\label{fig:treedec}}
\end{figure}
